High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-03-02 inst/manuscript/manuscript.Rmd
MS edited through methods

---
title: "High resolution, annual maps of the characteristics of small-scale croplands at national extents"

@@

- name: \*Provisional author list\*
  affilnum: '1'

- name: Lyndon D. Estes
  affilnum: '1'
  email: lestes@clarku.edu

@@

- name: Dennis McRitchie
  affilnum: '2'

@@

- name: Kelly Caylor
  affilnum: '3'

- name: Stephanie Debats
  affilnum: '4'

- name: Justus Muhando
  affilnum: '5'

- name: SpatialCollective
  affilnum: '5'

@@

- affilnum: 2
  affil: Dennis and Sons, Tucson, AZ, USA

- affilnum: 3
  affil: UCSB

- affilnum: 4
  affil: Uber

- affilnum: 5
  affil: SpatialCollective

- affilnum: 6
  affil: Meridia

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

@@

# Introduction
Amidst all the challenges posed by global change, a particular concern is how agriculture will adapt to meet humanity's growing food demands, and the impacts that a transforming and expanding agriculture will have on societies, economies, and environment [@searchingerCreatingSustainableFood2019]. Significant efforts are being made to address the various aspects of this challenge, including work on  diagnosing and closing yield gaps [e.g. @LickerMindgaphow2010; @lobellCropYieldGaps2009; @muellerClosingYieldGaps2012], expanding and commercializing production [@morrisAwakeningAfricaSleeping2009], and to understand [@davisTropicalForestLoss2020; @kehoeNatureRiskFuture2017; @RulliFoodappropriationlarge2014] and mitigate [@EstesReconcilingagriculturecarbon2016] agriculture's ecological impacts. The ability to answer the questions these efforts seek to address depends on data that describes the location and nature of cropland, and how that is changing over time. Unfortunately, the data that do exist are in many places inaccurate. Existing estimates of how much cropland there is tend to vary widely, and they often disagree about where cropland is located [e.g. @FritzHighlightingcontinueduncertainty2011; @Fritzneedimprovedmaps2013]. These discrepancies are due to the fact that cropland data in many regions are derived from remotey sensed landcover maps, which can be notoriously high in error, particularly over regions such as Africa [@Esteslargeareaspatiallycontinuous2018; @FritzComparisonglobalregional2010], where agricultural changes will be largest and the need for accurate baseline data is thus greatest [@EstesReconcilingagriculturecarbon2016; @SearchingerHighcarbonbiodiversity2015; @bullockThreeDecadesLand2021]

@@

Cropland mapping over a region such as Africa is difficult for several reasons. The primary reason relates to the characteristics of the region's smallholder-dominated croplands, where field size averages 1-2 ha [@Debatsgeneralizedcomputervision2016; @FritzMappingglobalcropland2015]. This size is small relative to the 30-250 m resolution of the sensors typically used for most landcover mapping efforts, which results in errors due to mixed pixels and aspects of the modifiable area unit problem [@Openshawmillioncorrelationcoefficients1979], in this case the pixel's shape may be poorly matched to that of cropland, and is too coarse to aggregate to approximate that shape at the characteristic scales of crop fields [@Darkmodifiablearealunit2007; @Esteslargeareaspatiallycontinuous2018]. On top of the matter of scale is 1) high intra-class variability of the cropland class, compounded by the fact that these particular croplands can be heavily intergraded with surrounding vegetation [@Debatsgeneralizedcomputervision2016; @Estesplatformcrowdsourcingcreation2016], and 2) the substantial temporal variability within croplands, both within and between seasons. These latter two aspects pose challenges for the classification algorithms that are applied to the imagery.

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This spatial and temporal resolution addresses the sensor-scale mismatch, and more effectively captures the intra-seasonal dynamics of cropland, which helps classifiers distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017], the opening of image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are placing large volumes of these moderate to near-high resolution imagery together with the computational and algorithmic resources necessary to classify them at scale. These capabilities are aleady being used to create a new generation of higher resolution (20-30 m) cropland and landcover maps for Africa and other regions [@ChenGloballandcover2015; @ESAESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

Despite these advances, the highest resolution (<5 m) image sources are still not used to map cropland over very large extents, presumably because they are commercial and relatively high cost to acquire, in addition to the greater computational demands. As such, map accuracy can still be a challenge, particular for user's accuracy, which ranges between 46 and 76% for for the cropland class [e.g. @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

Accuracy may also suffer due to error-inducing factors that are becoming somewhat more pronounced as a consequence of these technology advances, particularly with respect to algorithms. Advances in machine learning are helping to greatly improve classification skill, but these algorithms generally require large training datasets [@MaxwellImplementationmachinelearningclassification2018], particularly deep-learning methods (cite). To satisfy this need for more training (and reference) samples, map-makers increasingly rely on visual interpretation of high resolution satellite or aerial imagery to collect training (or validation) samples [e.g. @XiongNominal30mCropland2017; @ChenGloballandcover2015; @StehmanKeyissuesrigorous2019]. Several web-based platforms have been developed to facilitate such efforts, which provide convenient and highly scalable tools for training data collection [e.g. @BeyCollectEarthLand2016; @Estesplatformcrowdsourcingcreation2016; @FritzGeoWikionlineplatform2012]. Visually interpreted training labels present two particular problems. The first is that such labels have inevitable interpretation errors that can vary substantially according to the skill of the interpreter [@Estesplatformcrowdsourcingcreation2016; @WaldnerConflationexpertcrowd2019]. These errors are typically not accounted for in reported accuracy metrics, despite the fact that they can introduce substantial error into the resulting maps and subsequent analyses [@ElmesAccountingtrainingdata2020; @Esteslargeareaspatiallycontinuous2018]. The second problem is that visual interpretation depends on high resolution imagery (<5 m), as lower resolutions make it difficult for a human analyst to discern cropland. Typically the only practical source for such imagery are "virtual globe" basemaps provided by Microsoft and Google, which are composed of mosaics of various high resolution satellite and aerial image sources that typically span 3-5 years of time within a single country [@LesivCharacterizingspatialtemporal2018]. This within-mosaic temporal variation can set up a temporal mismatch between the imagery being interpreted and the imagery being classified, which are usually from a different source (e.g. Landsat, Sentinel; @XiongNominal30mCropland2017) and often represent a different year. If a land change occurs in the interval between the two image sets (e.g. a new field was created), this can introduce error into the training data that is then passed on to the classifier. This source of error may be elevated in smallholder-dominated systems, where swidden practices are common (cite), or in rapidly developing agricultural frontiers [@ZengHighlandcroplandexpansion2018].  
<!-- - Why cropland mapping is hard -->
<!--     - 3 problems -->
<!--         - The target itself and its spectral variability and the spectral variability of its background -->
<!--             - Spectral and spatial resolution of sensors -->
<!--             - Poses a challenge for classification algorithms, which want both high resolution to be smaller than characteristic field size, but temporal contrast also -->

To improve the accuracy of cropland maps over smallholder-dominated systems therefore requires an approach that meets three requirements. First, it should be based on high spatial and temporal resolution imagery, to be able to capture the fine grain and temporal variability of these fields. Second, an algorithm with suitable skill for classifying these images must be selected, and combined with the computational resources needed to process large imagery volumes. Third, a method for collecting large volumes of high quality training and validation data based on image interpretation is essential. This method should quantify and minimize the errors associated with image interpretation. It should also ensure that labels are collected either from the same imagery that is being classified, or from contemporanous imagery, in order to reduce errors introduced by land change processes.

<!-- - Training data dependence issues -->
<!--     - Also interact with image resolution issues -->
<!--     - Increasingly rely on high amounts of training data -->
<!--     - Human interpretation error (training data quality) -->
<!--       - Temporal mismatch with classification feedstock (Lesiv paper) -->
<!--       - Errors in interpreting these sources of imagery -->
<!-- - Review of who does what to solve the problem (probably integrated with problem statement) -->
<!--   - croplands.org -->

We describe here a cropland mapping system that addresses these requirements on the way to delineating field boundaries. The first requirement is enabled by the recent availability of cubesat data that provides 3-4 m resolution imagery over large areas at near daily intervals [@McCabefutureEarthobservation2017]. Although these data are of lower spectral depth and quality than Landsat, Sentinel, or Worldview imagery, they enable country-continent scale image mosaics to be created for multiple periods during the crop growing calendars, and this representation of intra-annual variability is more important for cropland classification than spectral depth [@Debatsgeneralizedcomputervision2016]. Their daily revisit capacity also is important for being able to develop cloud-free, sub-annual composites in cloudy regions.    Additionally, despite this imagery being up to ~16 times coarser than much of Bing or Google imagery, it is sufficiently resolved for humans to discern most fields [e.g. see @Esteslargeareaspatiallycontinuous2018; @FourieBetterCropEstimates2009]. This allows labels to be generated on the same imagery processed by the classifier, thereby addressing one of the two needs related to training data (requirement 3). The second requirement is addressed by a computer vision/machine learning classifer that is effective for classifying smallholder croplands [@Debatsgeneralizedcomputervision2016] and was re-engineered to run on high performance, cloud-based computing clusters. This classifier is tightly coupled to a front-end platform for collecting label data, which includes rigorous accuracy assessment protocols [@Estesplatformcrowdsourcingcreation2016] and a novel approach for merging multiple maps into consensus labels, thereby minimizing image interpretation error. The training and machine learning components are combined within an "active learning" framework, wherein the machine learning process assesses classification uncertainty in unlabelled areas after a training step, and selects sites from areas of highest uncertainty for additional labelling [@DebatsIntegratingactivelearning2017]. Our framework automates and formalizes this interactive approach to label selection, which has been shown to be important for improving accuracy in previous studies [e.g. @XiongNominal30mCropland2017; others add]. Furthermore, it is more efficient than purely randomized or conventionally stratified approaches to label collection, meaning that fewer labels are needed to generate a given level of accuracy [@DebatsIntegratingactivelearning2017]. Finally, an unsupervised segmentation step is applied to the imagery and merged with the pixel-wise classifications from the machine learning process, **resulting in a further sharpening of accuracy** and resulting in a final vector-based field boundary map.

We demonstrate this approach to map cropland in Ghana, a country where agriculture is predominantly small-scale and comprises a broad mix of agricultural systems, including large areas where shifting agricultural practices predominate [@KansangaTraditionalagriculturetransition2019; @SambergSubnationaldistributionaverage2016]. These factors make Ghana emblematic of the substantial challenges facing cropland mapping over the broader region.

<!-- - Our approach that tries to solve these three problems -->
<!-- - Within a framework that tightly integrates tightly training data collection -->
<!-- - And handles large-scale computation -->
<!-- - Segmented boundaries -->

# Methods
## System overview 
The mapping system is centered around four components: 1) an image acquisition and compositing component, 2) a training data collection platform, 3) a machine learning component, and 4) a segmentation component. The first component is applied as a once-off step to generate an image catalog covering the mapping geography, while the second component initiates an interactive image training and classification (component 3) pipeline that results in a pixel-wise posterior probability map of cropland probabilities on its final iteration (Fig. 1). The final segmentation step (component 4) is then initiated and applied to both the pre-processed primary images and the posterior probability maps, resulting in vectorized field boundaries. Each system component comprises an individual software module designed to be implemented on cloud computing architecture, and available on a GitHub repository (see data and software availability section for details).

## System components
### Imagery
**[Note: This will require updating to reflect changes to compositing methods]**
The primary image source used in our system is the PlanetScope Analytic surface reflectance product [@PlanetTeamPlanetApplicationProgram2017], although it can be readily adapted to apply to other images (e.g. Sentinel and Landsat). PlanetScope provides three visual (red, green, blue) and a near-infrared band at 3-4 m resolution at nominal daily frequency. Although these images are already pre-preprocessed and corrected for atmospheric effects, there are residual errors from inter-sensor differences and the radiometric normalization process [@HouborgDailyRetrievalNDVI2018], variation in the orientation of scene footprints, as well as a high frequency of cloud cover over the study region [@WilsonRemotelySensedHighResolution2016]. To correct for these factors, we developed a procedure for creating temporal composites representing the primary growing and non-growing seasons within a single year.

```{r aois, echo = FALSE, out.width="50%", fig.cap="An overview of the primary system components, the data stores that hold the inputs and outputs from each component, and the direction of connections between them. The dashed line indicates iterative interactions, while solid lines indicate one-time or irregular connections.", fig.align='center'}
knitr::include_graphics('figures/figure1.png')
```

PlanetScope imagery is accessed via the Planet API, and an initial order is placed wherein the imagery representing all available dates in the two compositing periods and within a bounding box covering the mapping geography is collected and transferred directly to the system's cloud storage (Amazon Web Services S3).

We then transform all images into an "analysis ready data" (ARD) product [@DwyerAnalysisReadyData2018] that is prepared against a tiling grid that is situated within a larger 1 degree resolution grid that covers the entire continent. Each 1 degree cell defines the minimum mapping area of interest (Fig. 2A) is divided into 400 0.05 degree cells (Fig. 2B), which provides the scale for creating image composite tiles. The ARD process simply clips all available imagery to the extent of each 0.05 cell it intersects, regardless of cloud cover.

@@

```{r, echo = FALSE, out.width="100%", fig.cap="The reference system used in the mapping platform, including A) numbered areas of interest (AOIs) that define the minimum mapping geography (solid black lines; dotted lines indicate boundaries of 1 degree grid), B) the 0.05 degree tile used for compositing imagery, and C) the 0.005 degree resolution reference grid used for collecting training data and distributed computing.", fig.align='center'}
knitr::include_graphics('figures/figure2.png')
```
The temporal compositing process is applied to the ARD imagery for the time period of interest, which in the case of this study is one of two multi-month seasons, the primary growing and dry seasons for a single agricultural year. Imagery from two seasons helps to improve the performance of cropland classifiers [@Debatsgeneralizedcomputervision2016], while having the seasons in same year helps to minimize differences caused by land change. For each pixel in each image in each ARD temporal stack for a given season, we calculate two weights, with the first being:

@@

And the second:

@@

Where *t* is a particular date in near-daily time series of PlanetScope images, which begins at date 1 for the given compositing period and ends on date *i*, *blue* is the blue band, and *NIR* the near infrared band.Equation \ref{eq:cloud} assigns lower weights to hazy and clouded pixels as the blue band is sensitive to haze and cloud pixels [@Zhangimagetransformcharacterize2002], while equation \ref{eq:shadow} assigns low weights to pixels in cloud shadow considering the significant darkening effect of the cloud shadows in the Near Infrared band [@ZhuObjectbasedcloudcloud2012; @qiuCirrusCloudsThat2020]

Once these two weights were calculated, the final composited pixel value for each of the four PlanetScope bands was calculated as:

@@

Which is a weighted mean for each pixel for each band *B* for the particular compositing period. The composited tiles were then added to the S3 store (Fig. 1), where they are stored as cloud-optimized geotiffs, and a "slippy map" rendering is created for each composite using RasterFoundry (cite). This web-based rendering of the image is used in the training data platform (see **section X**).

### Labelling platform
Both training and reference data were collected by a custom crowdsourcing platform, which we refer to here for simplicity's sake as *labeller*. The original version of *labeller* was designed to work with Amazon Web Services' Mechanical Turk job marketplace [@Estesplatformcrowdsourcingcreation2016]. The basic structure of the system remains the same, but we have re-engineered it into a standalone platform that 1) allows us to enroll and pay workers (the human supervisors) directly to conduct digitizing work, and 2) drives and assesses the overall machine learning process. The system runs on a Linux Virtual machine hosted on an AWS EC2 instance and is comprised of a database (PostGIS/Postgres), a mapping interface (OpenLayers 3), an image server (RasterFoundry), and a set of utilities for managing mapping and assessing assignments and converting them to rasterized labels for the machine learning process. Each *labeller* instance is focused on a specific mapping geography (e.g. one to several 1 degree cells in Fig. 2A)

Here we provide an overview of *labeller*'s architecture.

#### Mapping workflow
##### Selecting training and reference sites
The labelling process begins with a python script that randomly selects a subset (e.g. 100) of the 0.005 degree grid (Fig. 2C) cells that intersect the *labeller* instance's specific area of interest (e.g. shaded grey cell in Fig. 2A). These site names are stored in a Postgres table with the PostGIS extension that represents the mapping queue. Another python process converts each site into a mapping *task* that has a specified number of *assignments* (maps drawn by an individual worker) that must be completed before the task is complete.

##### Mapping assignments
Workers registered in the system log in to the mapping platform (built with Flask) and navigate to the OpenLayers-based field mapping interface (Fig. 3). There the worker is presented with a white target box representing the 0.005 degree cell that was randomly selected to label, a set of digitizing tools, and different image backdrops, which include false and true color "slippy map" renderings (generated by Raster Foundry) of both the growing season and off-growing season PlanetScope images covering that cell, as well as basemap imagery provided by Bing and ESRI. The worker uses the polygon drawing tool to digitize the boundaries in crop fields visible within the PlanetScope overlays that intersect the grid target, following a set of pre-defined digitizing rules. To aid with interpretation, the worker toggles between the various seasonal renderings and the satellite base map to help form a judgement about what constitutes a field within the PlanetScope imagery. The worker assigns each completed polygon a label that describes the field class (e.g. annual cropland, tree crop, fallow), and after completing all visible fields saves the full set of polygons to the server. The worker is then automatically taken to their next assignment at a different randomly selected site.

```{r, echo = FALSE, out.width="100%", fig.cap="An overview of mapper's interface", fig.align='center'}
knitr::include_graphics('figures/figure3.png')
```

>>>>

---
title: "High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales"

@@

- name: Lyndon Estes
  affilnum: '1'
  email: lestes@clarku.edu

@@

- name: Dennis McRitchie
  affilnum: ''

- name: Stephanie Debats
  affilnum: ''

- name: Justus Muhando
  affilnum: '2'

@@

- name: Kelly Caylor
  affilnum: '3-5'

@@

- affilnum: 2
  affil: SpatialCollective

- affilnum: 3
  affil: Department of Geography, University of California Santa Barbara, Santa Barbara, CA, USA

- affilnum: 4
  affil: Earth Research Institute, University of California Santa Barbara, Santa Barbara, CA, USA

- affilnum: 5
  affil: Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA, USA

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
csl: ecology.csl

@@

# Introduction
Amidst all the challenges posed by global change, a particular concern is how agriculture will adapt to meet humanity's growing food demands, and the impacts that a transforming and expanding agriculture will have on societies, economies, and environment [@searchingerCreatingSustainableFood2019]. Significant efforts are being made to address the various aspects of this challenge, including work on  diagnosing and closing yield gaps [e.g. @LickerMindgaphow2010; @lobellCropYieldGaps2009; @muellerClosingYieldGaps2012], expanding and commercializing production [@morrisAwakeningAfricaSleeping2009], and to understand [@davisTropicalForestLoss2020; @kehoeNatureRiskFuture2017; @RulliFoodappropriationlarge2014] and mitigate [@EstesReconcilingagriculturecarbon2016] agriculture's ecological impacts. Answering many of the questions these efforts seek to address depends on reliable data that describes the location and characteristics of cropland [@FritzMappingglobalcropland2015], and how these are changing over time. Unfortunately, the data that do exist are in many places inaccurate or missing. Existing estimates of how much cropland there is tend to vary widely, and they often disagree about where cropland is located [e.g. @FritzHighlightingcontinueduncertainty2011; @Fritzneedimprovedmaps2013]. Such errors can propagate in subsequent analyses that rely on cropland data as inputs, resulting in potentially misleading answers [@Esteslargeareaspatiallycontinuous2018]. Beyond cropland distributions, few data are available on cropland characteristics such as field size, which provide important information on agricultural systems  [@lesivEstimatingGlobalDistribution2019]. These inadequacies are due to the fact that cropland data in much of the world are derived from remotely sensed landcover maps, which can be notoriously high in error, particularly over regions such as Africa [@Esteslargeareaspatiallycontinuous2018; @FritzComparisonglobalregional2010], where agricultural changes will be largest and the need for accurate baseline data is thus greatest [@EstesReconcilingagriculturecarbon2016; @SearchingerHighcarbonbiodiversity2015; @bullockThreeDecadesLand2021]

@@

Cropland mapping over Africa is difficult for several reasons. The primary reason relates to the characteristics of the contintent's smallholder-dominated croplands, where half of all fields are smaller than 1 ha [@lesivEstimatingGlobalDistribution2019]. This size is small relative to the 30-250 m resolution of the sensors typically used in many landcover mapping efforts [e.g. @ChenGloballandcover2015; @sulla-menasheHierarchicalMappingAnnual2019], which results in errors due to mixed pixels and aspects of the modifiable area unit problem [@Openshawmillioncorrelationcoefficients1979]. In the latter case, the pixel's shape may be poorly matched to that of cropland, and is too coarse to aggregate to approximate that shape at the characteristic scales of crop fields [@Darkmodifiablearealunit2007; @Esteslargeareaspatiallycontinuous2018]. On top of the matter of scale is 1) high intra-class variability of the cropland class, compounded by the fact that these particular croplands can be heavily intergraded with surrounding vegetation [@Debatsgeneralizedcomputervision2016; @Estesplatformcrowdsourcingcreation2016], and 2) the substantial temporal variability within croplands, both within and between seasons. These latter two aspects pose challenges for the classification algorithms that are applied to the imagery.

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This high spatial *and* temporal resolution addresses the sensor-scale mismatch, and more effectively captures the intra-seasonal dynamics of cropland, which helps classifiers distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017], the opening of image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are placing large volumes of these moderate to near-high resolution imagery together with the computational and algorithmic resources necessary to classify them at scale. These capabilities are aleady being used to create a new generation of higher resolution (10-30 m) cropland and landcover maps for Africa and other regions [@ESAESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

Despite these advances, the highest resolution (<5 m) image sources are still not used to map cropland over very large extents, presumably because they are commercial and relatively high cost to acquire, in addition to the greater computational demands. As such, map accuracy can still be a challenge, particular for User's accuracy, which ranges between 46 and 76% for the cropland class [e.g. @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

Accuracy may also suffer due to error-inducing factors that are becoming somewhat more pronounced as a consequence of these technology advances, particularly with respect to algorithms. Advances in machine learning are helping to greatly improve classification skill, but these algorithms generally require large, high-quality training datasets [@ElmesAccountingtrainingdata2020; @maDeepLearningRemote2019; @MaxwellImplementationmachinelearningclassification2018]. To satisfy this need for more training (and reference) samples, map-makers increasingly rely on visual interpretation of high resolution satellite or aerial imagery to collect training (or validation) samples [e.g. @XiongNominal30mCropland2017; @ChenGloballandcover2015; @StehmanKeyissuesrigorous2019]. Several web-based platforms have been developed to facilitate such efforts, which provide convenient and highly scalable tools for training data collection [e.g. @BeyCollectEarthLand2016; @Estesplatformcrowdsourcingcreation2016; @FritzGeoWikionlineplatform2012]. Visually interpreted training labels present two particular problems. The first is that such labels have inevitable interpretation errors that can vary substantially according to the skill of the interpreter [@Estesplatformcrowdsourcingcreation2016; @WaldnerConflationexpertcrowd2019]. These errors are typically not accounted for in reported accuracy metrics, despite the fact that they can introduce substantial error into the resulting maps and subsequent analyses [@ElmesAccountingtrainingdata2020; @Esteslargeareaspatiallycontinuous2018]. The second problem is that visual interpretation depends on high resolution imagery (<5 m), as lower resolutions make it difficult for a human analyst to discern cropland. Typically the only practical source for such imagery are "virtual globe" basemaps provided by Microsoft and Google, which are composed of mosaics of various high resolution satellite and aerial images that typically span 3-5 years of time within a single country [@LesivCharacterizingspatialtemporal2018]. This within-mosaic temporal variation can set up a temporal mismatch between the imagery being interpreted and the imagery being classified, which is usually from a different source (e.g. Landsat, Sentinel; @XiongNominal30mCropland2017). If a land change occurs in the interval between the two image sets (e.g. a new field was created), this can introduce error into the training data that is then passed on to the classifier. This source of error may be elevated in smallholder-dominated systems in the tropics, where swidden practices are common [@vanvlietThereContinuingRationale2013], or in rapidly developing agricultural frontiers [@ZengHighlandcroplandexpansion2018].

Improving the accuracy of cropland maps over smallholder-dominated systems thus requires an approach that meets three requirements. First, it should be based on high spatial and temporal resolution imagery, to be able to capture the fine grain and temporal variability of smallholders' fields. Second, an algorithm with suitable skill for classifying these images must be selected, and combined with the computational resources needed to process large imagery volumes. Third, a method for collecting large volumes of high quality training and validation data based on image interpretation is essential. This method should quantify and minimize the errors associated with image interpretation. It should also ensure that labels are collected either from the same imagery that is being classified, or from contemporanous imagery, in order to reduce errors introduced by land change processes.

We describe here a cropland mapping system that follows these requirements on the way to delineating field boundaries. The first requirement is enabled by the recent availability of CubeSat data that provides 3-4 m resolution imagery over large areas at near daily intervals [@McCabefutureEarthobservation2017]. Although these data, currently collected by Planet's CubeSat fleet, are of lower spectral depth and quality than Landsat, Sentinel, or Worldview imagery, they enable country to continental scale image mosaics to be created for multiple periods during the crop growing calendars, and capturing the intra-annual variability can be more important for classifying cropland than spectral depth [@Debatsgeneralizedcomputervision2016]. This daily revisit capacity is also important for developing seasonal composites in cloudy regions, where satellites with longer return intervals may fail. Lastly, although this imagery being up to ~16 times coarser than much of Bing or Google imagery, it is sufficiently resolved for humans to discern most fields [e.g. see @Esteslargeareaspatiallycontinuous2018; @FourieBetterCropEstimates2009]. This allows labels to be generated on the same imagery processed by the classifier, thereby addressing one of the two needs related to training data (requirement 3).

The second requirement is addressed by a computer vision/machine learning classifer that is effective for classifying smallholder croplands [@Debatsgeneralizedcomputervision2016], re-engineered to run on high performance, cloud-based computing clusters, and following recommended practices for controlling for and measuring the errors that occur when training machine learning models for remote sensing applications [@ElmesAccountingtrainingdata2020]. The classifier is tightly coupled to a front-end platform for collecting label data, which includes rigorous accuracy assessment protocols and a novel approach for merging multiple maps into consensus labels, thereby minimizing image interpretation error [@Estesplatformcrowdsourcingcreation2016; @ElmesAccountingtrainingdata2020]. The training and machine learning components are combined within an "active learning" [@cohnImprovingGeneralizationActive1994] framework, wherein the machine learning process assesses classification uncertainty in unlabelled areas after a training step, and selects sites from areas of highest uncertainty for additional labelling [@DebatsIntegratingactivelearning2017]. Our framework automates this interactive approach to label selection, which has been shown to be important for improving accuracy in previous studies [e.g. @XiongNominal30mCropland2017]. Furthermore, it is more efficient than purely randomized or conventionally stratified approaches to label collection, meaning that fewer labels are needed to generate a given level of accuracy [@cohnImprovingGeneralizationActive1994; @DebatsIntegratingactivelearning2017]. Finally, an unsupervised segmentation step is applied to the imagery and merged with the pixel-wise classifications from the machine learning process, resulting in a final vector-based field boundary map that provides important information on field geometry.

We demonstrate this approach to map cropland in Ghana, a country where agriculture is predominantly small-scale and comprises a broad mix of climates and agricultural systems, including large areas where shifting agricultural practices predominate [@KansangaTraditionalagriculturetransition2019; @SambergSubnationaldistributionaverage2016]. These factors make Ghana emblematic of the substantial challenges facing cropland mapping over the broader region.

# Methods
## System overview 
The mapping system design has four primary components focused on 1) image acquisition and compositing, 2) training and validation data collection, 3) image classification, and 4) segmentation. The first component is applied as a once-off step to generate an image catalog covering the mapping geography. The second component provides tools for labelling imagery, and controls an interactive model training and classification (component 3) pipeline that produces a map of cropland probabilities for each image pixel (Figure \ref{fig:systemoverview}). The final segmentation step (component 4) is then initiated and applied to both the input image catalog and the posterior probability maps, resulting in vectorized field boundaries. Each system component comprises an individual software module designed to be implemented on cloud computing architecture, and available on a GitHub repository (see data and software availability section for details).

```{r systemoverview, echo = FALSE, out.width="50%", fig.cap="An overview of the primary system components, the data stores that hold the inputs and outputs from each component, and the direction of connections between them. The dashed line indicates iterative interactions, while solid lines indicate one-time or irregular connections.", fig.align='center'}
knitr::include_graphics('figures/figure1.png')
```

## System components
### Image compositing
The image processing components of our system was designed to work with PlanetScope Analytic surface reflectance data [@PlanetTeamPlanetApplicationProgram2017]. PlanetScope provides three visual (red, green, blue) and a near-infrared band at 3-4 m resolution at nominal daily frequency. Although these images are already pre-preprocessed and corrected for atmospheric effects, there are residual errors from inter-sensor differences and the radiometric normalization process [@HouborgDailyRetrievalNDVI2018], variation in the orientation of scene footprints, as well as a high frequency of cloud cover over the study region [@WilsonRemotelySensedHighResolution2016]. To correct for these factors, we developed a procedure for creating temporal composites representing the primary growing and non-growing seasons within a single year.

PlanetScope imagery is accessed via the Planet API, and an initial order is placed for all imagery falling within the mapping geography and the date ranges for the two compositing periods. The imagery is collected and transferred directly to the system's cloud storage (Amazon Web Services [AWS] S3).

Individual images are then transformed into "analysis ready data" (ARD) [@DwyerAnalysisReadyData2018], by cropping each downloaded scene into a 0.05 degree tile, regardless of cloud cover. Tiles are organized within a larger 1 degree resolution grid that covers the entire continent, which defines the minimum mapping area of interest (AOI; Figure \ref{fig:aois}).

@@

```{r aois, echo = FALSE, out.width="100%", fig.cap="The reference system used in the mapping platform, including A) numbered areas of interest (AOIs) that define the minimum mapping geography (solid black lines; dotted lines indicate boundaries of 1 degree grid), B) the 0.05 degree tile used for compositing imagery, and C) the 0.005 degree resolution reference grid used for collecting training data and distributed computing.", fig.align='center'}
knitr::include_graphics('figures/figure2.png')
```
The temporal compositing process is applied to the tiled daily images for the time period of interest, which in this case was one of two multi-month seasons, the primary growing and dry seasons for a single agricultural year. Imagery from two seasons helps to improve the performance of cropland classifiers [@Debatsgeneralizedcomputervision2016], while having the seasons in same year helps to minimize differences caused by land change. For each pixel in each image in each ARD temporal stack for a given season, two weights are calculated:

@@

@@

Where *t* is a particular date in near-daily time series of PlanetScope images, which begins at date 1 for the given compositing period and ends on date *i*, *blue* is the blue band, and *NIR* the near infrared band. Equation \ref{eq:cloud} assigns lower weights to hazy and clouded pixels as the blue band is sensitive to haze and cloud pixels [@Zhangimagetransformcharacterize2002], while Equation \ref{eq:shadow} assigns low weights to pixels in cloud shadow considering the significant darkening effect of the cloud shadows in the Near Infrared band [@ZhuObjectbasedcloudcloud2012; @qiuCirrusCloudsThat2020]

Once these two weights are calculated, the final composited pixel value for each of the four PlanetScope bands is:

@@

Which is a weighted mean for each pixel for each band *B* for the particular compositing period. The composited tiles were then added to the S3 store (Figure \ref{fig:systemoverview} 1), where they are stored as cloud-optimized geotiffs, and a "slippy map" rendering is created for each composite using Raster Foundry$\footnote{https://github.com/raster-foundry/raster-foundry}$. The web-rendered imagery is presented within the training data platform (next section).

### Labelling platform
Training and reference data are collected by a custom labelling platform, which was originally designed for AWS's Mechanical Turk job marketplace [@Estesplatformcrowdsourcingcreation2016]. The basic structure of the system remains the same, but we converted it into a standalone platform that allows us to enroll and pay people directly for their labelling, and is designed to control and supervise the machine learning process. The platform runs on a Linux virtual machine hosted on an AWS EC2 instance and is comprised of a database (PostGIS/Postgres), a mapping interface (OpenLayers 3), an image server (RasterFoundry), and a set of utilities for managing, assessing, and converting digitization work into rasterized labels for training a machine learning algorithm. Each instance of the platform focuses on a specific AOI (Figure \ref{fig:aois}A)

The following sections provide an overview of the labelling platform's architecture.

#### Mapping workflow
##### Selecting training and reference sites
The labelling process begins with the random selection of a subset (e.g. 500) of cells from a 0.005 degree grid, with the selection itself potentially split into a training and validation sample, according to predetermined proportions. The grid, which is nested within the tiling and larger 1 degree grids (Figure \ref{fig:aois}C) defines the spatial unit for a labelling job. The selected cells are placed into a queue within the platform's database, and then converted into a mapping *task* that has a specified number of *assignments* (boundaries drawn by an individual labeller) that must be completed before the task is complete.

##### Mapping assignments
Labellers registered in the system log in to the mapping platform (built with Flask) and navigate to the OpenLayers-based field mapping interface (Figure \ref{fig:labeller}), where they are presented with a white target box representing the randomly selected grid cell, a set of digitizing tools, and different image backdrops, including true and false color renderings of the the growing season and off-growing season PlanetScope composites, and several virtual globe basemaps. Following a set of pre-defined digitizing rules, the labeller uses the polygon drawing tool to digitize the boundaries of all crop fields intersecting the target grid cell that are visible within the PlanetScope overlays. To aid with interpretation, the labeller can toggle between the PlanetScope renderings and the basemaps to help form a judgement about what constitutes a field. The labeller assigns each polygon a field class category (e.g. annual cropland, tree crop, fallow), and upon completing all fields submits the assignment to the database. In cases where the target grid cell does not contain any fields, the labeller simply submits the assignment to mark it complete. The labeller is then directed to the next available assignment from a different labelling task.

```{r labeller, echo = FALSE, out.width="100%", fig.cap="An overview of mapper's interface", fig.align='center'}
knitr::include_graphics('figures/figure3.png')
```
